decompr: trade flow decomposition for Global Value Chain analysis

### 2014-12-01 README.Rmd
add non eval
update str to dims
add discussion wwz to intro

The decomposition of gross trade flows solves this problem,
by reallocating the value of intermediate goods used by industries to the original producers.
In our example, the use of Argentinian agricultural produce (raw hides)
is subtracted from the Turkish leather industry and added to the Argintinian agricultural industry.

@@

```{r manual-import}
final_demand <- read.csv( file             = "final_demand.csv",
                          header           = FALSE,
                          stringsAsFactors = FALSE               )

@@

```{r source-eval}
str(source)
```

Discussion
------------------------

Acknowledgements
--------------------
FNS
Fei Wang

References
----------------------

>>>>

The source decomposition of gross trade flows solves this problem,
by reallocating the value of intermediate goods used by industries to the original producers.
In our example, the use of Argentinian agricultural produce (raw hides)
is subtracted from the Turkish leather industry and added to the Argintinian agricultural industry.

The Wang-Wei-Zhu decomposition goes a step further by not only revealing the source of the value added,
but also breaking down exports into different categories, based on final usage.

* domestic value added - absorbed abroad
* domestic value added - eventually reimported
* foreign value added
* pure double counted terms

The decompr package implements the algorithms for these decompositions as R procedures.

The next section introduces the data as it is used by the package,
as well as an example data set provided by the WIOD.
Section three summarises the theoretical derivation for the decompositions,
and shows how these can be performed in R using the package.
After which we conclude with a discussion of potential uses and limitations of this approach.

@@

```{r manual-import, eval=FALSE}
final_demand <- read.csv( file             = "final_demand.csv",
                          header           = FALSE,
                          stringsAsFactors = FALSE               )

@@

```{r source-eval}
dim(source)
```

Discussion
=============

Acknowledgements
==================
FNS
Fei Wang

References
============
